---
title: "5922_T1"
author: "Abby Jia"
date: "02/08/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(GGally)
```

```{r readdata}
Swiss_Export <- readRDS("SwissExport.rds")
```


## Produce a histogram of the exports in December 2018

```{r plot, echo=TRUE}
qplot(ExportsDec2018, data = Swiss_Export)
# qplot(Swiss_Export$ExportsDec2018)
```
The above plot shows right skewed. There are two outliers in 3e+09

## Produce a scatterplot of January 1988 exports against December 2018 exports
```{r plot, echo=TRUE}
qplot(ExportsJan1988,ExportsDec2018, data = Swiss_Export)
#qplot(Swiss_Export$ExportsJan1988, Swiss_Export$ExportsDec2018))
```

The above plot shows positive relationship. There are two outliers in top 3e+09 andright 9e+08
因为左下角的点都聚集在一起，it is hard to observe whether there is a linear relationship between these two variables.

10. Log transform thoes values
# Log transform
log_exp1988=log(Swiss_Export$ExportsJan1988)
log_exp2018=log(Swiss_Export$ExportsDec2018)

# Plot scatter chart
qplot(log_exp1988,log_exp2018)
通过将原本的两个variable log，再plot出来可以看出there is a positive linear relationship between these two variables.Than


```{r}
# T3_Using the Swiss Export Data, plot a bar chart of the region variable
ggplot(Swiss_Export,aes(x=Region))+geom_bar()
```

```{r}
# T3_Construct a density plot, rug plot and boxplot for Exports in January 1988

## density plot
ggplot(Swiss_Export,aes(x=ExportsJan1988))+geom_density()

## rug plot (Useless)
ggplot(Swiss_Export,aes(x=ExportsJan1988))+geom_rug()

## Box plot (将x转换成y)
ggplot(Swiss_Export,aes(y=ExportsJan1988))+geom_boxplot()
```

```{r}
#scatterplot
ggplot(Swiss_Export,aes(x=ExportsJan1988,y=ExportsDec2018))+geom_point()

ggplot(Swiss_Export,aes(x=ExportsJan1988,y=ExportsDec2018))+geom_point()+scale_x_log10()+scale_y_log10()
# The warning due to log(0)
```
```{r}
credit = readRDS("Credit.rds")
```

```{r}
# Using box plots, explore whether the distribution of age is different for the default group and non-defaultgroup. Interpret your resul

ggplot(credit,aes(x=default,y=AGE))+geom_boxplot()
#
ggplot(credit,aes(x=default,y=AGE))+geom_boxplot(notch = T)
```
notch is overlapping,there is no significanr difference. There is no clear relationsip between age and default


```{r}
# Using box plots, explore whether the distribution of the credit limit (LIMIT_BAL) is different for thedefault group and non-default group. Interpret your result

ggplot(credit,aes(x=default,y=LIMIT_BAL))+geom_boxplot()
#
ggplot(credit,aes(x=default,y=LIMIT_BAL))+geom_boxplot(notch = T)
```

notch is not overlapping. There is significant difference between . There is a relatipnship between 


# Lecure 5
```{r}
data(diamonds)
# price greater than 2000 and carat less than 3.
exe1 <- diamonds %>%
  filter((price>2000)&(carat<3))
exe1

# price greater than 2000 and cut either Very Good, Premium or Ideal.
exe2 <- diamonds %>%
  filter((price>2000) & (cut %in% c('Very Good', 'Premium','Ideal')))
exe2

# carat less than 2 or price greater than 500.
exe3 <- diamonds %>%
  filter((carat<2) | (price>500))
exe3

# carat less than 2 and cut not equal to Premium.
exe4 <- diamonds %>%
  filter((carat<2) & (cut != 'Premium'))
exe4
```

```{r}
mpgSel <- mpg %>%
  select(mpg,cty,hwy) %>%
  mutate(ctyMetric=0.425144*cty,
         hwyMetric=0.425144*hwy)
```

```{r}
# In the diamonds dataset, find the average price for each cut of diamond.
p41exe1 <- diamonds %>%
  group_by(cut) %>%
  summarise(Totavg = mean(price, na.rm = TRUE))
p41exe1

#In the diamonds dataset, find the average price for each cut of diamond given that price in above 2000.
p41exe2 <- diamonds %>%
  filter(price > 2000) %>%
  group_by(cut) %>%
  summarise(avgprice = mean(price, na.rm = TRUE))
p41exe2

#In the mpg dataset find the average fuel efficiency in the city of in each year.
p41exe3 <- mpg %>%
  group_by(year) %>%
  summarise(avgfuel = mean(cty))
p41exe3

#In the mpg dataset, consider Toyota, Nissan and Honda. Find the value of hwy for each of these manufacturer's most fuel efficient cars on the highway.
p41exe4 <- mpg %>%
  filter(manufacturer %in% c('toyota','nissan','honda'))%>%
  group_by(manufacturer) %>%
  summarise(avgfuel_h = mean(hwy)) 
p41exe4
```

# Tutorial_W5
```{r}
# Read the data into R
SwissExFul <- read_csv("SwissExportsFull.csv")

# A column name is `NA` cannot be recognized, thus R automatically rename the column name as `X154`
# change back to `NA` fron X154
SwissExFul <- SwissExFul%>%rename(`NA`=X154)
view(SwissExFul$`NA`)

#Gather all countries into one column named `country`
long <- pivot_longer(data=SwissExFul,
                     cols=c(-Date,-Year),# except `Date` & `Year`columns, others column all pivot_longer
                     names_to = 'country', 
                     values_to = 'exports')
long

# Using group_by and summarise create a new dataset of yearly aggregate exports to each country
swissyearly <- long %>%
  group_by(Year, country) %>%
  summarise(yearlyexports=sum(exports))
swissyearly

# Produce a scatterplot on a log-log scale of 1988 exports against 2018 exports
swissyearlywide=swissyearly%>%
  filter(Year%in% c(1988, 2018))%>%
  pivot_wider(id_cols = country,names_from=Year,values_from=yearlyexports)
swissyearlywide

ggplot(swissyearlywide, aes(x=`1988`, y=`2018`))+geom_point()+scale_x_log10()+scale_y_log10()
# Because the data include 0 value, thus it has warning message

# Produce the same plot but remove all countries for which exports are zero in either 1988 or 2018.
swissyearlywide %>%
  filter((`1988`!= 0)&(`2018`!=0)) %>%
  ggplot(aes(x=`1988`, y=`2018`))+geom_point()+scale_x_log10()+scale_y_log10()

```

```{R}
# Read the data from this csv file into R
apple <- read_csv("apple_options.csv")

#The `Implied Volatility` column has been imported as a character variable. To plot this it must be converted toa numeric variable. Create this using themutatefunction.
apple <- apple %>%
  mutate(IV=gsub('%','',`Implied volatility`) %>% as.numeric/100)
apple
# first``是被代替的内容
# second``是代替的内容
# third``是from which column


# 3. The volatility smile is best observed when options with a single expiry date are used. To use as much data as possible, find the expiry date that has the most put options.
appleoption_put <- apple%>%
  filter( Type=='Put')%>%
  group_by(`Expiry date`)%>%
  summarise(no_options=n())


# 4.Options that are very farout of the money(very low strike price for a put option) should be excluded from the analysis. Building on previous answers, construct a data frame that only keeps put options from the expiry date in your answer to Question 3, and that have a strike price above 250.
appleoption <- apple%>%
  filter((Type=='Put')&(`Strike Price` > 250))%>%
  group_by(`Expiry date`,`Strike Price`)%>%
  summarise(no_options=n())

# 5.Using the data constructed in Q4, find the median value of Implied Volatility for each Strike Price.
applemeidan <- apple%>%
  filter((Type=='Put')&(`Strike Price` > 250))%>%
  group_by(`Expiry date`,`Strike Price`)%>%
  summarise(median(IV))

# 6.Plot Implied Volatility against Strike Price using a line plot.
ggplot(apple, aes(x=IV, y=`Strike Price`))+geom_line()
```

```{r}
library(rvest)
html <- read_html('https://au.finance.yahoo.com/quote/AAPL/options?straddle=false')
tab <- html_table(html)
print(tab[[1]])

```


# W6_Lecture
```{r p36}
data(txhousing)
ggplot(txhousing,aes(x=sales, y=median)) + 
  geom_point()+
  facet_grid(rows = vars(year), cols = vars(month))

ggplot(txhousing,aes(x=sales, y=median)) + 
  geom_point()+
  facet_grid(~year)

ggplot(txhousing,aes(x=sales, y=median)) + 
  geom_point()+
  facet_wrap(~year)
```


# W6_Tutorial

```{r}
long_filter <- long %>%
  group_by(Year) %>%
  filter(country %in% c('DE','US','CN','IN')) %>%
  ggplot(aes(x=Year, y=exports))+
  geom_line()+
  facet_wrap(~country)
long_filter
```


```{r}
# Read data
USState <- readRDS("USStateData.rds")

# 1. Construct a bubble chart of income per capita (x axis) against life expectancy (y axis). The size of the bubble should reflect the State population, and the color should reflect the region
ggplot(USState,aes(x=Income, y=`Life Exp`,col=Region,size=Population))+
  geom_point()

# 3. Add the state abbreviations as text on the plot
ggplot(USState,aes(x=Income, y=`Life Exp`,col=Region,size=Population,label=Abbreviation))+
  geom_text()

# 4. If you are not satisfied with your anwser to question 6, redo the question. Hint: you may need to specifysome aesthetics within a geom.

# 5.The file `USStateRed.rds` contains the same data but with the variables State, Abbreviation, Frost, Murder and HS Grad stripped out. Load this data and plot a ggpairs plot.
USRed <- readRDS("USStateRed.rds") 
ggpairs(USRed)

# 6.Discuss some interesting features of the plot
```